Automatically Splitting a Two-Stage Lambda Calculus

### 2016-01-09 paper/examples.tex
small fixes

`2`datatype list2 = Empty2 | Cons2 of int * list2
fun tmap2 (f,()) ((l,q), p : tree) =
  let fun m Empty2 = Empty2
        | m (Cons2(h,t)) = Cons2(f ((l,h), p), m t) 
  in m q
val mapqss2 = tmap2 (qs2, ())`
\end{lstlisting}
%
Indeed, observe that the argument \texttt{f} of \texttt{qs1} is called only once,
whereas the corresponding argument \texttt{f} in \texttt{qs2} is evaluated once per element in \texttt{q}.

>>>>

`2`datatype list2 = Empty2 | Cons2 of int * list2
fun tmap2 (f,()) ((l,q), p : tree) =
  let fun m Empty2 = Empty2
        | m (Cons2(h,t)) = Cons2(f ((l,h), p), m t) 
  in m q
val mapqss2 = tmap2 (qs2, ())`
\end{lstlisting}
%
Indeed, observe that the argument \texttt{f} (for which \texttt{qs1} is later substituted) of \texttt{tmap1} is called only once,
whereas the corresponding argument \texttt{f} (for which \texttt{qs2} is later substituted) in \texttt{tmap2} is evaluated once 
per element in the query list \texttt{q}.
